---
title: "Customer Clustering and Attrition Analysis"
author: Davidmac Olisa Ekeocha
date: 2024-08-15
output: html_notebook
---
# Set a working directory
```{r}
# set working directory
setwd(dir = "C:/Users/david/OneDrive/Documents/ULMS/PhD/Jobs/src/career_track/ds_projects/customer_clustering/")
```
# load libraries
```{r}
library(tidyverse)
library(ggplot2)
#======================================================================================================================#
# One of the key challenges in multivariate data analysis and predictive modeling is effectively managing redundant
# and irrelevant variables. To tackle redundancy, a strategic approach involves identifying groups of variables that
# exhibit strong correlations within themselves while remaining as uncorrelated as possible with other groups in the
# dataset. Addressing relevancy, on the other hand, focuses on evaluating potential predictor variables by
# understanding the relationship between the target variable and the input variables.
#
# Multiple Correspondence Analysis (MCA) is a powerful multivariate data analysis tool used to uncover and visually
# represent associations among groups of categorical variables in a low-dimensional space. It is particularly effective
# in exploring complex relationships and patterns within categorical data. Variable clustering, often employed as a
# preliminary step, helps identify redundancy and offers an initial understanding of the data's multivariate structure.
#
# I aim to demonstrate the practical applications of MCA in three key areas: 1) preparing input variables for
# analysis and predictive modeling, 2) utilizing MCA as an exploratory tool for gaining business insights, such as
# understanding customer churn, and 3) applying variable clustering to identify and manage redundant categorical
# variables.
#
# In this analysis, we focus on customer churn data—a critical metric that businesses use to track and quantify the
# loss of customers or clients for various reasons. The dataset includes detailed customer-level information, such as
# demographics, account details, service usage, monthly charges, and the duration of their relationship with the
# company. The last column, labeled "churn," indicates whether a customer has left the company for a competitor (Yes)
# or remained with the company (No).
```
# load and pre-process the data
```{r}
churn <- readr::read_csv(file = "customer_churn.csv")
str(churn)
colnames(churn) <- tolower(colnames(churn))
glimpse(churn)

## check for factor levels in each column
factor_cols <- churn %>%
  select_if(is.character) %>%
  names() %>%
  .[. != "customerid"]
apply(churn %>% select(all_of(factor_cols)), MARGIN = 2, function(x) nlevels(as.factor(x)))
#======================================================================================================================#
# The dataset contains a total of 7043 customers and 21 customer attributes. The data structure shows that some
# variables need to be recoded and converted to factors. For instance, multiplelines, onlinesecurity, onlinebackup,
# deviceprotection, techsupport, streamingmovies, and streamingtv. Also, I will recode seniorcitizen to be a "Yes" or
# "No" for consistency. I use the below code to achieve the recoding.
#======================================================================================================================#
churn <- churn %>%
  mutate(
	multiplelines = case_when(multiplelines == "Yes" ~ "Yes",
							  multiplelines == "No" | multiplelines == "No phone service" ~ "No"),
	onlinesecurity = case_when(onlinesecurity == "Yes" ~ "Yes",
							   onlinesecurity == "No" | onlinesecurity == "No phone service" ~ "No"),
	onlinebackup = case_when(onlinebackup == "Yes" ~ "Yes",
							 onlinebackup == "No" | onlinebackup == "No phone service" ~ "No"),
	deviceprotection = case_when(deviceprotection == "Yes" ~ "Yes",
								 deviceprotection == "No" | deviceprotection == "No phone service" ~ "No"),
	techsupport = case_when(techsupport == "Yes" ~ "Yes",
							techsupport == "No" | techsupport == "No phone service" ~ "No"),
	streamingtv = case_when(streamingtv == "Yes" ~ "Yes",
							streamingtv == "No" | streamingtv == "No phone service" ~ "No"),
	streamingmovies = case_when(streamingmovies == "Yes" ~ "Yes",
								streamingmovies == "No" | streamingmovies == "No phone service" ~ "No"),
	contract = case_when(contract == "Month-to-month" ~ "Month_to_Month",
						 contract == "One year" ~ "One_Year",
						 contract == "Two year" ~ "Two_Years"),
	paymentmethod = case_when(paymentmethod == "Electronic check" ~ "Electronic_Check",
							  paymentmethod == "Mailed check" ~ "Mailed_Check",
							  paymentmethod == "Bank transfer (automatic)" ~ "Bank_Transfer",
							  paymentmethod == "Credit card (automatic)" ~ "Credit_Card"),
	internetservice = case_when(internetservice == "DSL" ~ "DSL",
								internetservice == "Fiber optic" ~ "Fiber_Optic",
								internetservice == "No" ~ "No"),
	seniorcitizen = ifelse(test = seniorcitizen == 1, yes = "Yes", no = "No"),
  )


factor_cols <- churn %>%
  select_if(is.character) %>%
  names() %>%
  .[. != "customerid"]
apply(churn %>% select(all_of(factor_cols)), MARGIN = 2, function(x) nlevels(as.factor(x)))
glimpse(churn)
```
# Summary statistics to get the data distribution
```{r}
ggplot(data = churn, aes(x = monthlycharges)) + geom_boxplot()
ggplot(data = churn, aes(x = monthlycharges)) + geom_histogram()

ggplot(data = churn, aes(x = tenure)) + geom_boxplot()
ggplot(data = churn, aes(x = tenure)) + geom_histogram()

summary(churn$monthlycharges)
summary(churn$tenure)
#======================================================================================================================#
# Based on the above summary statistics, I recode the the tenure and monthlycharges into three categories.
#======================================================================================================================#
churn <- churn %>%
  mutate(
	tenure_cat = as.factor(
	  case_when(tenure <= 9 ~ "Short_Tenure",
				tenure > 9 & tenure <= 29 ~ "Medium_Tenure",
				tenure > 29 ~ "Long_Tenure")
	),
	monthlycharges_cat = as.factor(
	  case_when(monthlycharges <= 35.5 ~ "Low_Charges",
				monthlycharges > 35.5 & monthlycharges <= 70.35 ~ "Medium_Charges",
				monthlycharges > 70.35 ~ "High_Charges")
	),

  )
```
# Check and convert character string columns to factors. Drop totalcharges column
```{r}
string_cols <- churn %>% select_if(is.character) %>% names()
churn[, string_cols] <- lapply(churn[, string_cols], as.factor)

drop_cols <- c("customerid", "totalcharges", "monthlycharges", "tenure")
churn <- churn %>%
  select(-all_of(drop_cols)) %>%
  select(churn, everything())
```
# Checking and Handling missing values
```{r}
# The code shows that 7% of the rows have missing values, a total of 9156 NAs.
# After removing the missing values, we have a total of 5517 rows.
apply(churn, MARGIN = 2, function(x) sum(is.na(x)))
mean(is.na(churn))
sum(is.na(churn))

# remove all NA rows
churn <- na.omit(churn) # zero missing values
```
# Now the data is ready for analysis
# Exploring churn
```{r}
ggplot(data = churn, aes(x = churn)) +
  geom_bar(fill = "darkblue") +
  labs(title = "Customer Attrition",
	   x = "Churn",
	   y = "Count")
```
# Split into train and test sets
```{r}
#======================================================================================================================#
# Partitioning the data into 80% training and 20% test sets based on churn. Set seed to make results reproducible.
# The training data contains 4414 observations and 19 columns and the testing data contains 1103 observations and 19
# columns.
#======================================================================================================================#
# load the required library
library(caret)

set.seed(seed = 123)
in_train <- caret::createDataPartition(churn$churn, p = 0.8, list = FALSE)
training <- churn %>% slice(in_train)
testing <- churn %>% slice(-in_train)

dim(training)
dim(testing)
```
# Multiple Correspondence Analysis (MCA)
```{r, fig.width = 20, fig.height = 20}
#======================================================================================================================#
# Invoke the FactoMiner & factoextra packages.
#======================================================================================================================#
library(FactoMineR)
library(factoextra)

# Apply MCA
res_mca <- MCA(X = training, quali.sup = c(15, 17, 19), graph = F)
fviz_mca_var(res_mca, repel = T)
#----------------------------------------------------------------------------------------------------------------------#
# To derive business insights from the figure above, a useful approach is to observe and note the proximity of input
# variables to the target variable, as well as their closeness to one another. For example, the figure above shows that
# customers who are senior citizens, those that uses Fiber optic internet services, and those on high-
# charges, paperless billing, with multiple lines and phone services, but no dependents or partner, no online security
# or backup, no device protection or tech-support, are more associated with customers on a medium tenure and
# month-to-month contract, have higher likelihood to churn.

# In contrast, non-senior citizen customers on long-term contract and between one to two years tenure, with partners,
# online backup and device protection are less likely to churn.
```
# Clustering
```{r}
#======================================================================================================================#
# Load the ClustOfVar package and the hclustvar function produces a tree of variable groups.
#======================================================================================================================#
library(ClustOfVar)

# run variable clustering excluding the target variable (churn)
variable_tree <- hclustvar(X.quali = as.matrix(training[, 2:18]))
# plot the dendrogram of variable groups
plot(variable_tree)
#----------------------------------------------------------------------------------------------------------------------#
# There appear to be 6 distinct variable groups in the dendrogram. This is based on the number of distinct clusters
# formed at the highest level of the tree. Since the distinct clusters are not explosive, there is no need to cut them.
# However, I show that the 6 clusters are indeed the desired number of cluster after B = 100 bootstrap samples. I use
# the
# stability function from the ClustOfVar package to assess the stability of the variable cluster partitions.
#======================================================================================================================#
stability(tree = variable_tree, B = 100, graph = T)
#----------------------------------------------------------------------------------------------------------------------#
# The plot shows that the 4 optimal clusters are the desired number of clusters
#======================================================================================================================#
cut_cluster <- cutreevar(obj = variable_tree, k = 4)
print(cut_cluster$var)
#----------------------------------------------------------------------------------------------------------------------#
# The 6-clusters and the variable names in each cluster are listed below. The practical guide to minimizing redundancy
# is to select a cluster representative. However, subject-matter considerations should have a say in the consideration
# and selection of other candidate representatives of each variable cluster group.
#======================================================================================================================#
# Descriptive statistics of customer churn
# Determine the overall churn rate in the dataset. The overall churn rate is 32%.
#======================================================================================================================#
round(prop.table(table(churn$churn)) * 100, digits = 2)
```
# Customer attrition rate by demography
```{r, fig.height = 15}
demog_cols <- 2:19
demog_counts <- training %>%
  select(all_of(demog_cols), churn) %>%
  pivot_longer(cols = -churn, names_to = "class", values_to = "value") %>%
  group_by(class, value, churn) %>%
  tally(name = "counts") %>%
  pivot_wider(names_from = churn, values_from = counts, values_fill = 0) %>%
  mutate(churn_rate = round((Yes / (No + Yes) * 100) - 31.83, digits = 1)) %>%
  transmute(category = paste(class, value, sep = " -- "), churn_rate)

ggplot(demog_counts, aes(category, churn_rate, color = churn_rate < 0)) +
  geom_segment(aes(x = reorder(category, -churn_rate), xend = category,
				   y = 0, yend = churn_rate),
			   linewidth = 1.5, alpha = 2) +
  geom_point(size = 3) +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "brown")) +
  theme(legend.position = "none") +
  labs(x = "Variable",
	   y = "Customer Attrition (%)",
	   title = "Customer Attrition rate \n Difference from the overall average (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip()
demog_counts
#----------------------------------------------------------------------------------------------------------------------#
# The figure above shows that customer attrition rate is highest amongst customers who are senior citizens,without a
# partner, no device protection, no online backup, no tech-support, no online security, uses fibre-optic internet
# services, with monthly contract, electronic check payment method and on short tenure. Conversely, customers with
# one- to two-year contracts, online security, tech-support, long-tenure, pays with credit cards and bank transfers,
# non-senior citizens have dependents and partner, online backup and device protection have less attrition rates.
```
# Correlation matrix
```{r, fig.height = 20, fig.width = 20}
#======================================================================================================================#
# Converting factors to numeric.
#======================================================================================================================#
# Converting factors to numeric
dummies <- dummyVars(~., data = churn, fullRank = F, sep = "_")
churn_df <- predict(dummies, newdata = churn) %>%
  data.frame() %>%
  select(-contains(match = "No"))
head(churn_df)

# Correlation matrix
corrplot::corrplot(
  corr = cor(churn_df, method = "spearman"),
  method = "circle",
  type = "lower",
  tl.col = "black",
  tl.srt = 45,
  addCoef.col = TRUE
)
```
# Near zero variance features
```{r}
nzv <- nearZeroVar(x = churn_df, saveMetrics = TRUE)
filtered_nnzv <- nzv %>% filter(nzv == FALSE) # non-near zero variance
filtered_nnzv

filtered_nzv <- nzv %>% filter(nzv == TRUE) # near zero variance
filtered_nzv
remove_features <- rownames(filtered_nzv)

# Remove near zero variance features
churn_df <- churn_df %>% select(-all_of(remove_features))
```
# Find and remove Linear Dependences
```{r}
linear_combs <- findLinearCombos(x = churn_df)
linear_combs
churn_df <- churn_df %>% select(-all_of(linear_combs$remove))
```
# Split data into training and testing
```{r}
set.seed(seed = 123)
in_train <- createDataPartition(churn_df$churn_Yes, p = 0.8, list = FALSE)
training <- churn_df %>% slice(in_train)
testing <- churn_df %>% slice(-in_train)
```
# Prediting Attrition rates
```{r}
#======================================================================================================================#
# Prediting Attrition rates
# Logistic Regression
#======================================================================================================================#
model <- glm(
  formula = churn_Yes ~ .,
  data = training,
  family = "binomial"
)
summary(model)
#----------------------------------------------------------------------------------------------------------------------#
# Make Predictions on the Testing Data
#----------------------------------------------------------------------------------------------------------------------#
model_pred <- predict(model, newdata = testing)
range(model_pred)

model_df <- data.frame(
  actual = testing$churn_Yes,
  predicted = model_pred
) %>%
  mutate(
	actual = as.factor(ifelse(actual == 1, yes = "Yes", no = "No")),
	predicted_over_0.5 = as.factor(ifelse(predicted >= 0.5, yes = "Yes", no = "No"))
  )
```
# Confusion Matrix. And Accuracy
```{r}
conf_matrix <- model_df %>%
  yardstick::conf_mat(actual, predicted_over_0.5)
conf_matrix

conf_matrix <- model_df %>%
  dplyr::count(actual, predicted_over_0.5) %>%
  pivot_wider(names_from = predicted_over_0.5, values_from = n, values_fill = list(n = 0))
conf_matrix

# Calculate accuracy
# True positives and true negatives are in the diagonal
true_positives <- conf_matrix %>%
  filter(actual == "Yes") %>%
  pull(Yes)

true_negatives <- conf_matrix %>%
  filter(actual == "No") %>%
  pull(No)

total <- sum(conf_matrix$Yes) + sum(conf_matrix$No)
accuracy <- (true_positives + true_negatives) / total
print(paste("Accuracy:", round(accuracy * 100, digits = 0), "%"))
```
# Plot the ROC Curve and Calculate the AUC
```{r}
library(pROC)
library(ggplot2)

# Calculate the ROC curve
roc_obj <- roc(testing$churn, model_pred)

# Plot the ROC curve
ggroc(roc_obj, colour = "brown", linetype = 1, size = 2) +
  ggtitle(label = "ROC Curve") +
  labs(x = "Specificity", y = "Sensitivity") +
  geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), color = "grey", linetype = "dashed") +
  theme_bw()

# Calculate the AUC
auc_value <- round(auc(roc_obj), digits = 2)
print(auc_value)
```
# Ensemble Model method
```{r}
#======================================================================================================================#
# Model ensemble using caret
#======================================================================================================================#
# Prepare the data
churn_df <- churn_df %>%
  mutate(
	churn_Yes = as.factor(ifelse(churn_Yes == 1, yes = "Yes", no = "No")),
  )

# Get the predictors
labelName <- churn_df %>%
  select(churn_Yes) %>%
  names()
predictors <- churn_df %>%
  select(-c(all_of(labelName), churn_Yes)) %>%
  names()
```
# Splitting the data into ensembleData, blenderData and testData
```{r}
# Split the data into one-thirds
seed <- 123
set.seed(seed = seed)
churn_df <- churn_df %>% slice_sample(prop = nrow(.))
split <- floor(x = nrow(churn_df) / 3)
ensembleData <- churn_df %>% slice(1:split)
blenderData <- churn_df %>% slice((split + 1):(split * 2))
testData <- churn_df %>% slice((split * 2 + 1):n())
```
# Tuning the models
```{r}
# Load the necessary model library
names(getModelInfo())
library(gbm) # for gradient boosting
library(naivebayes)
library(caTools) # for boosted logit

# Define training control
my_ctrl <- trainControl(
  method = "repeatedcv",
  number = 10, # 10-folds cross-validation
  repeats = 10, # repeat 10 times using bootstrapping
  returnResamp = "none",
  classProbs = TRUE, # to get class probabilities
  summaryFunction = twoClassSummary # to estimate performance
)

# Tune GBM model
gbmTuned <- expand.grid(
  .n.trees = seq(from = 100, to = 1000, by = 100), # number of trees
  .interaction.depth = seq(from = 1, to = 7, by = 2), # depth of each tree
  .shrinkage = c(0.01, 0.1), # slow and fast learner
  .n.minobsinnode = 20 # minimum number of observations in each node of the tree.
)
```
# Training the models
```{r}
# GBM --- Stochastic Gradient Boosting
start_time <- Sys.time()
model_gbm <- train(
  x = ensembleData %>% select(all_of(predictors)),
  y = ensembleData %>% pull(labelName),
  method = "gbm",
  preProcess = c("center", "scale"),
  metric = "ROC",
  tuneGrid = gbmTuned,
  trControl = my_ctrl,
  verbose = FALSE
)
end_time <- Sys.time()
end_time - start_time
model_gbm
ggplot(model_gbm) + theme(legend.position = "top")

# Predict the testData
testData <- testData %>%
  mutate(
	actual = churn_Yes,
	gbm_Pred = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors))),
	gbm_Pred_No = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 1],
	gbm_Pred_Yes = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 2],
  )

# Confusion Matrix
confusionMatrix(testData$actual, testData$gbm_Pred, positive = "Yes")

# AUC Curve
gbm_auc <- roc(response = testData$actual,
			   predictor = as.numeric(testData$gbm_Pred),
			   levels = rev(levels(testData$actual)))
gbm_auc

# Plot the GBM ROC curve
gbm_auc_curve <- ggroc(gbm_auc, colour = "blue", linetype = 1, size = 2) +
  ggtitle(label = "GBM ROC Curve") +
  labs(x = "Specificity", y = "Sensitivity") +
  geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), color = "grey", linetype = "dashed") +
  theme_bw()
```
```{r}
# Treebag
model_treebag <- train(
  x = ensembleData %>% select(all_of(predictors)),
  y = ensembleData %>% pull(labelName),
  method = "treebag",
  preProcess = c("center", "scale"),
  metric = "ROC",
  # tuneGrid = tunedGrid,
  trControl = my_ctrl,
  verbose = FALSE
)
model_treebag

# Predict the testData
testData <- testData %>%
  mutate(
	actual = churn_Yes,
	gbm_Pred = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors))),
	gbm_Pred_No = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 1],
	gbm_Pred_Yes = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 2],
	treebag_Pred = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors))),
	treebag_Pred_No = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors)),
							  type = "prob")[, 1],
	treebag_Pred_Yes = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors)),
							   type = "prob")[, 2],
  )

# Confusion Matrix
confusionMatrix(testData$actual, testData$treebag_Pred, positive = "Yes")

# AUC Curve
treebag_auc <- roc(response = testData$actual,
				   predictor = as.numeric(testData$treebag_Pred),
				   levels = rev(levels(testData$actual)))
treebag_auc

# Plot the Treebag ROC curve
treebag_auc_curve <- ggroc(treebag_auc, colour = "blue", linetype = 1, size = 2) +
  ggtitle(label = "Treebag model ROC Curve") +
  labs(x = "Specificity", y = "Sensitivity") +
  geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), color = "grey", linetype = "dashed") +
  theme_bw()
```
```{r}

# Ada boost
model_ada <- train(
  x = ensembleData %>% dplyr::select(all_of(predictors)),
  y = ensembleData %>% pull(labelName),
  method = "ada", # random forest
  preProcess = c("center", "scale"),
  metric = "ROC",
  # tuneGrid = tunedGrid,
  trControl = my_ctrl,
  verbose = FALSE
)
model_ada
# ggplot(model_ada) + theme(legend.position = "top")

# Predict the testData
testData <- testData %>%
  mutate(
	actual = churn_Yes,
	gbm_Pred = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors))),
	gbm_Pred_No = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 1],
	gbm_Pred_Yes = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 2],
	treebag_Pred = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors))),
	treebag_Pred_No = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors)),
							  type = "prob")[, 1],
	treebag_Pred_Yes = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors)),
							   type = "prob")[, 2],
	ada_Pred = predict(object = model_ada, newdata = testData %>% select(all_of(predictors))),
	ada_Pred_No = predict(object = model_ada, newdata = testData %>% select(all_of(predictors)),
						  type = "prob")[, 1],
	ada_Pred_Yes = predict(object = model_ada, newdata = testData %>% select(all_of(predictors)),
						   type = "prob")[, 2],
  )

# Confusion Matrix
confusionMatrix(testData$actual, testData$ada_Pred, positive = "Yes")

# AUC Curve
ada_auc <- roc(response = testData$actual,
			   predictor = as.numeric(testData$ada_Pred),
			   levels = rev(levels(testData$actual)))
ada_auc

# Plot the Treebag ROC curve
ada_auc_curve <- ggroc(ada_auc, colour = "blue", linetype = 1, size = 2) +
  ggtitle(label = "Ada Boost model ROC Curve") +
  labs(x = "Specificity", y = "Sensitivity") +
  geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), color = "grey", linetype = "dashed") +
  theme_bw()
```
```{r}

# xgboost
model_xgboost <- train(
  x = ensembleData %>% select(all_of(predictors)),
  y = ensembleData %>% pull(labelName),
  method = "xgbTree", # advanced boosted trees
  preProcess = c("center", "scale"),
  metric = "ROC",
  # tuneGrid = tunedGrid,
  trControl = my_ctrl,
  verbose = FALSE
)
model_xgboost
plot(model_xgboost)

# Predict the testData
testData <- testData %>%
  mutate(
	actual = churn_Yes,
	gbm_Pred = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors))),
	gbm_Pred_No = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 1],
	gbm_Pred_Yes = predict(object = model_gbm, newdata = testData %>% select(all_of(predictors)), type = "prob")[, 2],
	treebag_Pred = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors))),
	treebag_Pred_No = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors)),
							  type = "prob")[, 1],
	treebag_Pred_Yes = predict(object = model_treebag, newdata = testData %>% select(all_of(predictors)),
							   type = "prob")[, 2],
	ada_Pred = predict(object = model_ada, newdata = testData %>% select(all_of(predictors))),
	ada_Pred_No = predict(object = model_ada, newdata = testData %>% select(all_of(predictors)),
						  type = "prob")[, 1],
	ada_Pred_Yes = predict(object = model_ada, newdata = testData %>% select(all_of(predictors)),
						   type = "prob")[, 2],
	xgboost_Pred = predict(object = model_xgboost, newdata = testData %>% select(all_of(predictors))),
	xgboost_Pred_No = predict(object = model_xgboost, newdata = testData %>% select(all_of(predictors)),
							  type = "prob")[, 1],
	xgboost_Pred_Yes = predict(object = model_xgboost, newdata = testData %>% select(all_of(predictors)),
							   type = "prob")[, 2],
  )

# Confusion Matrix
confusionMatrix(testData$actual, testData$xgboost_Pred, positive = "Yes")

# AUC Curve
xgboost_auc <- roc(response = testData$actual,
				   predictor = as.numeric(testData$xgboost_Pred),
				   levels = rev(levels(testData$actual)))
xgboost_auc

# Plot the Treebag ROC curve
xgboost_auc_curve <- ggroc(xgboost_auc, colour = "blue", linetype = 1, size = 2) +
  ggtitle(label = "Advanced Boosted Trees model ROC Curve") +
  labs(x = "Specificity", y = "Sensitivity") +
  geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), color = "grey", linetype = "dashed") +
  theme_bw()

# Combine all the ROC curves
library(patchwork)

roc_curves <- gbm_auc_curve +
  treebag_auc_curve +
  ada_auc_curve +
  xgboost_auc_curve +
  plot_annotation(title = "ROC Curves", tag_levels = "A")
roc_curves
```
# Predict the blenderData and testData to get the probabilities
